---
        title: "Week 4 assignment of Practical Machine Learning"
        author: "Raymond MF Ng"
        output:
          html_document:
            toc: TRUE
---

# Init

Import library and set random seed.

```{r}
library(caret)
set.seed(1000)
```

# Read data from CSV

Read data file and replace obviously error in data, for example \#DIV/0! , empty etc. Replace it with NA

```{r}
pml_raw <- read.csv("pml-training.csv", na.strings = c("NA", "", "#DIV/0!"))
pml_forecast <- read.csv("pml-testing.csv", na.strings = c("NA", "", "#DIV/0!"))
```

# Remove data of no use

It seems not make sense to use the user_name as one of the variable to predict the outcome, also random forest do not works if there are lots of repeat NA

```{r}
pml_raw <- subset(pml_raw, select = -user_name) 
pml_forecast <- subset(pml_forecast, select = -user_name)
```

Calculate the ratio of NA for column and remove those mostly na, in this case we keep those column where 90% is not NA

```{r}
naCols <- colSums(data.matrix(!is.na(pml_raw))) / nrow(pml_raw) 
pml_raw <- pml_raw[naCols > 0.1] 
pml_forecast <- pml_forecast[naCols > 0.1]
```

Remove the column 1-5 which is not related too (X raw_timestamp_part_1 raw_timestamp_part_2 cvtd_timestamp new_window).

```{r}
pml_cleanedRaw <- pml_raw[, -c(1,2,3,4,5)] 
pml_cleanedForecast <- pml_forecast[, -c(1,2,3,4,5)]
```

# The resulting columns are these

```{r eval=TRUE, echo=TRUE}
names(pml_cleanedRaw)
```

# Split train set and test set

Split the data by 70%, we keep 30% for testing

```{r}
pml_cleanedRaw$classe <- as.factor(pml_cleanedRaw$classe) 
inTrain <- createDataPartition(y = pml_cleanedRaw$classe, p = 0.7)[[1]] 
pml_train <- pml_cleanedRaw[inTrain, ] 
pml_test <- pml_cleanedRaw[-inTrain, ] 

modForest <- train(classe ~ ., data=pml_train, method = "rf")
```

# Watch the variables

All variables have contribute something to the predicition

```{r fig-margin, fig.margin=TRUE}
plot(varImp(modForest))
```

# Run model with test set to predict output

The confusion matrix have quite good prediction result with sensitivity and specificity both above 95%

```{r eval=TRUE, echo=TRUE}
predictForest <- predict(modForest, newdata=pml_test)
confusionMatrix(pml_test$classe, predictForest)
```
